Voting

### 2024-02-13 paper/paper.qmd
Updated capitalization on county names in dataset

---
title: "Voting"
author: "Emily Su"
thanks: "Data and code are available at: https://github.com/moonsdust/toronto-collisions. The replication on the Social Science Reproduction Platform can be found here: https://www.socialsciencereproduction.org/reproductions/c0db16d9-e70e-4bbc-85d2-f7137a0e8c47/index"
date: today
date-format: "YYYY MMMM D"
abstract: "Abstract."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

# Data {#sec-data}

The datasets were retrieved, simulated, cleaned, analyzed, and tested using the `R` programming language [@citeR], `tidyverse` [@citetidyverse], `haven` [@citehaven], `knitr` [@citeknitr], `janitor` [@citejanitor], `dplyr` [@citedplyr], `ggplot2` [@citeggplot2], `sf` [@citesf], `readr` [@citereadr], and `dataverse` [@citedataverse].

@@

# Referenced to figure out how to create map: https://roelandtn.frama.io/cours_r_pdm/mapping-with-r-and-sf.html
ggplot(cleaned_map_data) + 
  geom_sf(aes(fill = count)) + 
  theme_minimal() + 
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Number of 2016 US election voters across Texas counties without proper ID",
    subtitle = "Counties with labels have more than or equal to 500 voters without IDs",
    fill = "Number of voters"
    ) +
  # Changes the font of the title and removes the x and y axis 
  # Reference to figured out how to add labels to maps https://tmieno2.github.io/R-as-GIS-for-Economists/create-maps.html
  geom_sf_text(
    # Referenced code to figure out how to only show labels with certain values     
    # https://r-graph-gallery.com/275-add-text-labels-with-ggplot2.html 
    data = cleaned_map_data |> filter(count>=500),
    # Label is county name
    aes(label = county),
    check_overlap = TRUE,
    size = 2, 
    color = "pink"
    ) +
    theme(plot.title = element_text(size = 9, face = 'bold'), 
          plot.subtitle = element_text(size = 9),
          rect = element_blank(), 
          axis.text.x = element_blank(), 
          axis.text.y = element_blank(), 
          axis.ticks = element_blank(), 
          legend.title = element_text(size = 8),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()
          ) 
```

@@

## Tables from Results {#sec-tablesfromresults}
```{r}
#| label: tbl-votermap
#| tbl-cap: Number of United States election voters across Texas counties in 2016 without proper ID
#| echo: false
#| warning: false
#| message: false

>>>>

---
title: "Voting"
author: "Emily Su"
thanks: "Data and code are available at: https://github.com/moonsdust/toronto-collisions. The replication on Social Science Reproduction Platform can be found here: https://www.socialsciencereproduction.org/reproductions/c0db16d9-e70e-4bbc-85d2-f7137a0e8c47/index"
date: today
date-format: "YYYY MMMM D"
abstract: "Abstract."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

# Data {#sec-data}
## Source

## Methodology
The datasets were retrieved, simulated, cleaned, analyzed, and tested using the `R` programming language [@citeR], `tidyverse` [@citetidyverse], `haven` [@citehaven], `knitr` [@citeknitr], `janitor` [@citejanitor], `dplyr` [@citedplyr], `ggplot2` [@citeggplot2], `sf` [@citesf], `readr` [@citereadr], and `dataverse` [@citedataverse].

## Measurements

@@

# Referenced to figure out how to create map: https://roelandtn.frama.io/cours_r_pdm/mapping-with-r-and-sf.html
ggplot(cleaned_map_data) + 
  geom_sf(aes(fill = count)) + 
  theme_minimal() + 
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Number of 2016 US election voters across Texas counties without proper ID",
    subtitle = "Counties with labels have more than or equal to 500 voters without IDs",
    fill = "Number of voters"
    ) +
  # Changes the font of the title and removes the x and y axis 
  # Reference to figured out how to add labels to maps https://tmieno2.github.io/R-as-GIS-for-Economists/create-maps.html
  geom_sf_text(
    # Referenced code to figure out how to only show labels with certain values     
    # https://r-graph-gallery.com/275-add-text-labels-with-ggplot2.html 
    data = cleaned_map_data |> filter(count>=500),
    # Label is county name
    aes(label = county),
    check_overlap = TRUE,
    size = 2, 
    color = "white"
    ) +
    theme(plot.title = element_text(size = 9, face = 'bold'), 
          plot.subtitle = element_text(size = 9),
          rect = element_blank(), 
          axis.text.x = element_blank(), 
          axis.text.y = element_blank(), 
          axis.ticks = element_blank(), 
          legend.title = element_text(size = 8),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()
          ) 
```

@@

## Tables from Results {#sec-tablesfromresults}
```{r}
#| label: tbl-votermap
#| tbl-cap: Number of United States election voters across Texas counties in 2016 without IDs
#| echo: false
#| warning: false
#| message: false
